Robinson et al. 2020 Supplemental Information: Comparing the Radiocarbon and Tree-ring Records for the Upland US Southwest

### 2020-01-18 analysis/paper/Robinson2020.Rmd
initial commit

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# devtools::install_github("village-ecodynamics/villager")
# purrr::walk(c("magrittr",
#               "tidyverse",
#               "googledrive",
#               "sf",
#               "lwgeom",
#               "units",
#               "rcarbon"), 
#             devtools::install_cran)

packages <- c("magrittr",
              "tidyverse",
              "googledrive",
              "sf",
              "lwgeom",
              "units",
              "rcarbon",
              "villager"
)

purrr::walk(packages,
            library, 
            character.only = TRUE)

source("R/get_df.R")

@@

@@

```{r}
# Define the Bocinsky et al. 2016 study area
SWUS_bbox <- sf::st_bbox(c(xmin = -113,
                           xmax = -105,
                           ymin = 32,
                           ymax = 38), 
                         crs = 4326) %>%
  sf::st_as_sfc()

# Define the Phoenix Basin
# Defined as SW AZ counties, using the National Map small scale data
# "https://prd-tnm.s3.amazonaws.com/StagedProducts/Small-scale/data/Boundaries/countyp010g.gdb_nt00933.tar.gz" %>%
#   download.file(destfile="../data-raw/countyp010g.gdb_nt00933.tar.gz", 
#                 mode='wb')
# untar("../data-raw/countyp010g.gdb_nt00933.tar.gz",
#       exdir="../data-raw/countyp010g")
phx_basin <- "./data-raw/countyp010g/countyp010g.gdb/" %>%
  sf::st_read() %>%
  dplyr::filter(NAME %in% 
                  c("Maricopa",
                    "Pinal",
                    "Pima")) %>%
  sf::st_transform(4326) %>%
  sf::st_union()

# Read in the Bocinsky et al. 2016 tree ring data
radiocarbon_data <- #readr::read_csv("./data-raw/Radiocarbon/14C_Raw.csv") %>%
  readr::read_csv("./data-raw/Radiocarbon/0403_sbox_clean.csv") %>%
  # Convert to spatial object
  sf::st_as_sf(coords = c("Long","Lat"),
               crs = 4326) %>%
  # Crop to SWUS bounding box
  sf::st_intersection(SWUS_bbox) %>%
  # Remove Phoenix Basin dates
  sf::st_difference(phx_basin) %>%
  # Select salient columns
  dplyr::select(labnumber,
                date,
                sd,
                #diff,
                #d13,
                #mat,
                #Source,
                Site,
                SiteID) %>%
  dplyr::rename(Lab_Number = labnumber,
                Date_BP = date,
                SD = sd,
                # Diff = diff,
                # Material = mat,
                Site_Number = Site) %>%
  sf::st_intersection("./data-raw/countyp010g/countyp010g.gdb/" %>%
                        sf::st_read() %>%
                        sf::st_transform(4326) %>%
                        dplyr::mutate(County = paste(NAME, STATE, sep = ", ")) %>%
                        dplyr::select(County)) %T>%
  # Write the output to a new file (geojson)
  sf::write_sf("./data-derived/radiocarbon_data.geojson",
               delete_dsn = TRUE)

@@

ggplot() + 
  geom_sf(data = four_corners_states) +
  ggplot2::geom_raster(data = swus_hillshade_500m %>%
                         get_df(),
                       mapping = aes(x = x,
                                     y = y,
                                     alpha = ID),
                       na.rm = TRUE) +
  scale_alpha(range = c(0.8, 0),
              na.value = 0,
              limits = c(0,255),
              guide = "none") +
  geom_sf(data = four_corners_states,
          fill = NA) +
  geom_sf(data = SWUS_bbox,
          fill = NA) +
  geom_sf(data = dates,
          mapping = aes(shape = `Date Type`,
                        color = Date_BP),
          show.legend = "point") +
  scale_shape(
    name = 'Date Type',
    solid = FALSE,
    guide = guide_legend(position = "top",
                         direction = "horizontal",
                         title.position = "top",
                         label.position = "bottom")
  ) +
  viridis::scale_color_viridis(
    name = 'Year BP',
    limits = c(450,1450),
    breaks = c(450,1450),
    direction = -1,
    guide = guide_colorbar(position = "top",
                           direction = "horizontal",
                           title.position = "top",
                           label.position = "bottom",
                           reverse = TRUE)) +
  theme_map(16)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(Robinson2020)
```

@@

vep

@@

```{r}
# Read in the Bocinsky et al. 2016 tree ring data
radiocarbon_data <- #readr::read_csv("./data-raw/Radiocarbon/14C_Raw.csv") %>%
  readr::read_csv("./data-raw/Radiocarbon/0403_sbox_clean.csv") %>%
  # Convert to spatial object
  sf::st_as_sf(coords = c("Long","Lat"),
               crs = 4326) %>%
  # Crop to SWUS bounding box
  sf::st_intersection(SWUS_bbox) %>%
  # Remove Phoenix Basin dates
  sf::st_difference(phx_basin) %>%
  # Select salient columns
  dplyr::select(labnumber,
                date,
                sd,
                #diff,
                #d13,
                #mat,
                #Source,
                Site,
                SiteID) %>%
  dplyr::rename(Lab_Number = labnumber,
                Date_BP = date,
                SD = sd,
                # Diff = diff,
                # Material = mat,
                Site_Number = Site) %>%
  sf::st_intersection("./data-raw/countyp010g/countyp010g.gdb/" %>%
                        sf::st_read() %>%
                        sf::st_transform(4326) %>%
                        dplyr::mutate(County = paste(NAME, STATE, sep = ", ")) %>%
                        dplyr::select(County)) %T>%
  # Write the output to a new file (geojson)
  sf::write_sf("./data-derived/radiocarbon_data.geojson",
               delete_dsn = TRUE)

@@

ggplot() + 
  ggplot2::geom_sf(data = four_corners_states) +
  ggplot2::geom_raster(data = Robinson2020::swus_hillshade_500m,
                       mapping = ggplot2::aes(x = x,
                                              y = y,
                                              alpha = ID),
                       na.rm = TRUE) +
  ggplot2::scale_alpha(range = c(0.8, 0),
                       na.value = 0,
                       limits = c(0,255),
                       guide = "none") +
  ggplot2::geom_sf(data = four_corners_states,
                   fill = NA) +
  ggplot2::geom_sf(data = SWUS_bbox,
                   fill = NA) +
  ggplot2::geom_sf(data = dates,
                   mapping = aes(shape = `Date Type`,
                                 color = Date_BP),
                   show.legend = "point") +
  ggplot2::scale_shape(
    name = 'Date Type',
    solid = FALSE,
    guide = ggplot2::guide_legend(position = "top",
                                  direction = "horizontal",
                                  title.position = "top",
                                  label.position = "bottom")
  ) +
  viridis::scale_color_viridis(
    name = 'Year BP',
    limits = c(450,1450),
    breaks = c(450,1450),
    direction = -1,
    guide = ggplot2::guide_colorbar(position = "top",
                                    direction = "horizontal",
                                    title.position = "top",
                                    label.position = "bottom",
                                    reverse = TRUE)) +
  theme_map(16)
